Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
...

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $. The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.

@@

	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}

@@

		$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$

>>>>

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + 1 + o(1)) $. The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.

@@

	$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}

@@

		$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
